---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  message = F,
  warning = F,
  fig.height = 8,
  fig.width = 16,
  dpi = 72,
  cache = FALSE
)
```

# invivoSyn

<!-- badges: start -->
<!-- badges: end -->

The goal of invivoSyn is to evaluate synergy for in vivo tumor growth data. Synergy can be calculated based on AUC-based drug effect or linear mixed model. For effect based efficacy, two reference models can be selected: HSA (Highest Single Agent) or Bliss (Bliss Independence).
P-values are calculated for both synergistic effect and antagonism effect.

The package supports **N-drug combinations** (vehicle + N single-agent arms + 1 combo arm). `read_tv()` accepts explicit role arguments (`vehicle`, `singles`, `combo`) so the raw CSV can be in any row order, can contain extra non-participating treatments, and is no longer restricted to the canonical 4-arm layout.

## Live App

> **[https://hupharm.shinyapps.io/invivoSyn/](https://hupharm.shinyapps.io/invivoSyn/)** — try the hosted app directly in your browser, no local installation required.

## Shiny application

The bundled Shiny application accepts wide or long tumor-volume files, supports
multiple Combination arms with exact comparator mapping, and runs independent
Bliss or HSA TGI/AUC analyses for each Combination.

``` r
invivoSyn::run_invivoSyn_app()
```

For local development, load the package checkout first with
`devtools::load_all()`. For shinyapps.io deployment, install `invivoSyn` from a
reproducible remote source and verify dependencies with
`rsconnect::appDependencies("inst/shiny/invivoSyn")`.

## Installation

You can install the development version of invivoSyn from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("maobinchen/invivoSyn")
```

## Example

This is a basic example which shows you how to do synergy calculation

```{r example}
library(invivoSyn)

# Declare roles explicitly — row order in the CSV no longer matters, extra
# non-participating treatments are filtered out, and the resolved roles travel
# with the tibble for every downstream call.
tv <- read_tv(
  system.file("extdata", "test.csv", package = "invivoSyn"),
  vehicle = "Vehicle",
  singles = c("Rabusertib", "Irinotecan"),
  combo   = "Irinotecan+Rabusertib"
)

# AUC-based efficacy (median AUC ratio, stratified bootstrap)
AUC_lst <- get_mAUCr(tv, ci = 0.9, ci_type = "bca")
AUC_lst$bsAUC_df

# AUC-based synergy — Bliss and HSA reference models
bliss_synergy_AUC <- AUC_synergy(AUC_lst)
bliss_synergy_AUC
hsa_synergy_AUC   <- AUC_synergy(AUC_lst, method = "HSA", t = 21, ci = 0.9, ci_type = "bca")
hsa_synergy_AUC
```

### N-drug combinations

`singles` can be any character vector of length ≥ 2 — for a three-drug
combination supply three single-agent names and the combo arm:

```r
tv <- read_tv("triple_study.csv",
              vehicle = "PBS",
              singles = c("A", "B", "C"),
              combo   = "A+B+C")
AUC_synergy(get_mAUCr(tv))   # Bliss expected survival = prod(S_i)
```

All downstream functions (`AUC_synergy`, `lmm_synergy`,
`CombPDX_CI`, `global_CI_synergy`) iterate over the N singles automatically.
`lmm_synergy` warns when N > 3, since the full N-way interaction grows as 2^N − 1.


