---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  message = F,
  warning = F,
  fig.height = 8,
  fig.width = 12,
  dpi = 72,
  cache = FALSE
)
```

# invivoSyn

<!-- badges: start -->
<!-- badges: end -->

The goal of invivoSyn is to evaluate synergy for in vivo tumor growth data. Synergy can be calculated based on TGI/AUC based drug effect or linear mixed model. For effect based efficacy, three reference models can be selected, which are HSA (Highest Single Agent), Bliss(Bliss Independence) or RA(Response Addivity).

## Installation

You can install the development version of invivoSyn from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("maobinchen/invivoSyn")
```

## Example

This is a basic example which shows you how to do synergy calculation

```{r example}
library(invivoSyn)
tv <- LS_1034
TGI_lst <- getTGI(tv,17)
bliss_synergy_TGI <- TGI_synergy(TGI_lst)
TGI_lst_RTV <- getTGI(tv,17,tv_var='RTV') #TGI defition from CombPDX paper
bliss_synergy_TGI_RTV <- TGI_synergy(TGI_lst_RTV)
global_CI=global_CI_synergy(tv)
AUC_lst <- get_mAUCr(SNU_81, ci = 0.9, ci_type = "bca")
bliss_synergy_AUC <- AUC_synergy(AUC_lst)
```


